An example of extremely reproducible enrichment analysis.

### 2023-03-09 example.Rmd
working on docs

```{r,gs}

genesets2 <- read.gmt("ReactomePathways_2023-03-06.gmt")
gsets <- gmtPathways("ReactomePathways_2023-03-06.gmt")

>>>>

```{r,gs}
# from https://reactome.org/download/current/ReactomePathways.gmt.zip
genesets2 <- read.gmt("ReactomePathways_2023-03-06.gmt")
gsets <- gmtPathways("ReactomePathways_2023-03-06.gmt")
